CommonMind Consortium: DLPFC

### 2020-09-17 combined_analysis/diff.networks.Rmd
Update diff networks

dynamicColors = labels2colors(dynamicMods, colorSeq = colors())
tab = table(dynamicColors)
hist(tab)
```

@@

```{r modules.in.discovery, fig.width=8, fig.height=50}

>>>>

dynamicColors = labels2colors(dynamicMods, colorSeq = colors())
tab = table(dynamicColors)
hist(tab, xlab="Cluster size")
```

@@

```{r modules.in.discovery, fig.width=8, fig.height=25}
